---
title: "Georgia"
date: now
date-format: "MMM D HH:mm:ss A z"
author: 
- Joseph R. Loffredo, Mason Reece, Charles Stewart III
affiliation: Massachusetts Institute of Technology
page-layout: full

format:
  html:
    embed-resources: true
    minimal: true
    fig-format: jpeg
    toc: true
    toc-location: body
    toc-title: Jump to
    toc-depth: 1
    fig-width: 12
    echo: false
    message: false
    warning: false
    keep-md: false
    template-partials:
      - metadata.html
---

```{r}

source("scripts/util/globals.R")

suppressPackageStartupMessages({
  library(targets)
  library(tidyverse)
  library(gt)
  library(glue)
})

inline_hook <- function(x) {
  if (is.numeric(x)) {
    format(x, digits = 2, nsmall = 0, big.mark = ",")
  } else x
}
knitr::knit_hooks$set(inline = inline_hook)

options(scipen = 999)

tar_read(model_GA_NA) |> list2env(envir = .GlobalEnv) |> invisible()

```

## Recent Updates

Last update: `r prec_reported_any - read_file(glue("{PATH_DROPBOX}/24_general/{state}/prec_reported_any_{county}")) |> as.numeric()` new precincts reported at `r ymd_hms(timestamp) |> with_tz("US/Eastern")`.

```{r}

# update historical file
write_file(as.character(prec_reported_any), glue("{PATH_DROPBOX}/24_general/{state}/prec_reported_any_{county}"))

```

## How Many Votes Are In?

`r sum(pull(data_history, votes_precTotal_24))` **total** votes are in, `r 100*sum(pull(data_history, votes_precTotal_24)) / 4935487`% of the 2020 total

- We estimate the **final total turnout** will be `r summaries$votes_total_24_estimate` with uncertainty bounds [`r summaries$votes_total_24_lower` to `r summaries$votes_total_24_upper`]

`r sum(pull(filter(data_history, vote_mode=="Election Day"), votes_precTotal_24))` **Election Day** votes are in, `r 100*sum(pull(filter(data_history, vote_mode=="Election Day"), votes_precTotal_24)) / sum(pull(filter(data_history, vote_mode=="Election Day"), votes_precFinal_20), na.rm=TRUE)`% of the 2020 total

- We estimate the **final Election Day turnout** will be `r pull(filter(summaries_byMode, vote_mode == "Election Day"), votes_total_24_estimate)` with uncertainty bounds [`r pull(filter(summaries_byMode, vote_mode == "Election Day"), votes_total_24_lower)` to `r pull(filter(summaries_byMode, vote_mode == "Election Day"), votes_total_24_upper)`]

**Precincts reporting all modes**: `r prec_reported_all` out of `r prec_total` total precincts (`r 100*round(prec_reported_all / prec_total, 2)`%)

**Precincts reporting Election Day**: `r prec_reported_eday` out of `r prec_total` total precincts (`r 100*round(prec_reported_eday / prec_total, 2)`%)

## Vote Estimates

**Margin (Harris - Trump)**: `r 100*(summaries$demShare_estimate - summaries$repShare_estimate)`pp with uncertainty bounds [`r 100*(summaries$demShare_lower - summaries$repShare_lower)`pp to `r 100*(summaries$demShare_upper - summaries$repShare_upper)`pp]

**Change in Margin vs 2020**: `r 100*(summaries$swing_estimate)`pp with uncertainty bounds [`r 100*(summaries$swing_lower)`pp to `r 100*(summaries$swing_upper)`pp]

```{r tbl_mode}

summaries_byMode |> 
  mutate(
    across(c(contains("swing")), ~ scales::label_percent(accuracy = 0.01)(.x)),
    swing_24 = glue("{swing_estimate} [{swing_lower} to {swing_upper}]")
  ) |> 
  filter(vote_mode != "Provisional") |> 
  select(vote_mode, swing_24) |> 
  gt() |> 
  tab_style_body(
    style = cell_text(font = "Hack"),
    fn = \(x) TRUE
  ) |>
  cols_align(align = "center") |> 
  cols_label(
    vote_mode = "Vote Mode",
    swing_24 = "Change in Margin vs 2020"
  )

```


**Democrat**: `r summaries$demVotes_estimate` with uncertainty bounds [`r summaries$demVotes_lower` to `r summaries$demVotes_upper`]

**Republican**: `r summaries$repVotes_estimate` with uncertainty bounds [`r summaries$repVotes_lower` to `r summaries$repVotes_upper`]

### Cumulative Plot of Estimated Vote Share (Dem and Rep)

```{r}

tar_read(plot_voteShare_GA_NA)

```

### Cumulative Plot of Margin vs 2020

```{r}

tar_read(plot_margin2020_GA_NA)

```

## Estimated Turnout

### Cumulative Plot of Estimated Election Day Votes

```{r}

tar_read(plot_votesEDay_GA_NA)

```

### Cumulative Plot of Estimated Total Votes

```{r}

tar_read(plot_votesAll_GA_NA)

```


## County-level Results by Mode

```{r tbl_county_mode}

tar_read(tbl_countyMode_GA_NA)

```

## County-level Results

```{r tbl_county}

tar_read(tbl_county_GA_NA)

```


